Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-02 Paper/grass.tex
Abstract update

The spontaneous waving of marine grass is thought to be due to a Kelvin-Helmholtz instability resulting from an inflection point in the flow profile. We find that this inflection point
is located near the tip of grass canopy. Our analysis shows that flow in presence of grass become unstable not only through a mechanism of Kelvin-Helmholtz instability associated with 
inflection point but also through shear instability of flow above grass coupled with the porous flow through grass bed. We further show that in canopy with high submergence ratio
Kelvin-Helmholtz insatbility is damped due to grass drag.

>>>>

The spontaneous waving of marine grass is thought to be due to a Kelvin-Helmholtz instability resulting from an inflection point near the canopy top in the flow profile.
 Our analysis of flow through grass bed predicts a critical threshold condition for instability and associated waving frequency
which compares well with experimental observations. We show that in the limit of a dense grass bed, two distinct unstable modes (Mode-1, Mode-2) can be asymptotically distinguished.
while Mode-1 shares many characteristics with the Kelvin-Helmholtz instability where shear layer near canopy top plays a critical role, 
Mode-2 can be thought of as instability of inviscid flow with dense grass bed for which shear 
layer near grass tip doesn't play a critical role. We further show that in canopy with high submergence ratio
Kelvin-Helmholtz insatbility is damped due to grass drag. In the parameter regime typical of marine grass beds, the two modes merge and are indistinguishable.

% Our analysis shows that flow in presence of grass become unstable not only through a mechanism of Kelvin-Helmholtz instability associated with 
%inflection point but also through shear instability of flow above grass coupled with the porous flow through grass bed.
